Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-10 paper/paper.tex
Add some assumptions/problem definition

\section{Problem Description}
\subsection{Application Model}
\subsection{System Model}

@@

\subsection{Workflow-Aware DPDS (WA-DPDS)}
\subsection{Static Provisioning Static Scheduling (SPSS)}

% This is an example of how we can do algorithms
\begin{algorithm}
\caption{Admit DAGs}
\label{alg:admit}
\begin{algorithmic}[1]
\Procedure{AdmitDAGs}{$W,b,d$}
    \State $P\gets empty\ plan$
    \State $A\gets \emptyset$ \Comment{Set of admitted DAGs}
    \For{$w\ in\ W$}
        \State $P^\prime \gets$\ \Call{PlanDAG}{$w,P,d$}
        \If{$P^\prime\ is\ a\ valid\ plan$}
            \If{$Cost(P^\prime) \le b$}
                \State $P\gets\ P^\prime$ \Comment{Accept new plan}
                \State $A \gets A\ +\ w$ \Comment{Admit w}
            \EndIf
        \EndIf
    \EndFor
    \State \textbf{return} $P,A$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

>>>>

\section{Problem Description}
\subsection{Resource Model}
Describe the Amazon EC2 resource model. Instances are requested on-demand. Instance pricing is per-hour. Multiple VM types are available, but for this paper we focus on a single VM type because we assume that there will typically be one VM type with the best price/performance ratio for the application.

\subsection{Application Model}
The target applications for this paper are scientific workflows that can be modeled as Directed Acyclic Graphs (DAGs).

We assume that we have runtime estimates for each task in the workflow.

Currently we do not consider data sizes, but rather assume that data is stored in a shared cloud storage system such as Amazon S3 and that data transfer times are included in task runtime estimates. Further, data transfer times are equal across the VMs.

An ensemble consists of several related workflows. Each workflow is given a priority.

The goal is to complete as many workflows as possible given a budget and a deadline.

@@

\subsection{Workflow-Aware DPDS (WA-DPDS)}

\subsection{Static Provisioning Static Scheduling (SPSS)}

We assume that the workflows are very wide such that the critical path of any given workflow is much less than the deadline.

The approach is to schedule each workflow in the ensemble in priority order, rejecting any workflows that cannot be completed by the deadline or that cause the cost of the plan to exceed the budget. Once the plan is complete, then the workflows are executed according to the plan.

\begin{algorithm}
\caption{Plan Ensemble}
\label{alg:admit}
\begin{algorithmic}[1]
\Procedure{PlanEnsemble}{$W,b,d$}
    \State $P\gets empty\ plan$
    \State $A\gets \emptyset$ \Comment{Set of admitted DAGs}
    \For{$w\ in\ W$}
        \State $P^\prime \gets$\ \Call{PlanDAG}{$w,P,d$}
        \If{$P^\prime\ is\ a\ valid\ plan$}
            \If{$Cost(P^\prime) \le b$}
                \State $P\gets\ P^\prime$ \Comment{Accept new plan}
                \State $A \gets A\ +\ w$ \Comment{Admit w}
            \EndIf
        \EndIf
    \EndFor
    \State \textbf{return} $P,A$
\EndProcedure
\end{algorithmic} 
\end{algorithm}
